### 2023-02-08 text/ManuscriptDraft.Rmd
Edits to manuscript draft

**Detecting small objects and many of them: Using computer vision and deep learning to automate counting of collembola in petri dish samples**

@@

@@

>>>>

**Detecting small objects and many of them: Computer vision and deep learning enables high-throughput counting of collembola in petri dish samples**

@@

Requires manual counting of

Recent advances in computer vision and deep learning methods enable automation of image analysis including detection of objects of interest.

@@

Ecotoxiological laboratory studies on soil invertebrates deliver important assessments of compound toxicities.

Manual live counts problematic because of movement of individuals.
Counting based on images can alleviate this problem.
Images also allow validation of counts.
